\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-07 manuscript.Rmd
Aesthetic Updates

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

@@

```{r relscale, include=F, warning=F, message=F}
relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
```

```{r simscalep}
relevant.scale.data %>%
   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1:6, width = "2cm")
```

@@

## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam
```

@@

To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales. However, no scales specifically measuring the behavioral component of light exposure were found (Table \@ref(tab:simscalep)). Consequentially we pursued to introduce a new openly available scale to address this research gap. For this purpose an expert researcher panel from the fields of chronobiology, light research, neuroscience and psychology (including seven of the authors, see authors roles) generated and collected preliminary item ideas. Special attention was paid to design items circumscribed to assess light exposure *behavior* as opposed to subjective measurements of the light environment (cf.[@eklund1996development] & [@dianat2013objective]) and semi-quantitive assesments of light sources' illuminance (cf. [@bajaj2011validation]) in order to maintain content validity. In a collective effort the generated items were then peer-reviewed,  amended, unified, and complemented with a suitable response scale (5 point Likert-scale ranging from 1 "Never/Does not apply/I don’t know" to 5 "Always"). This process was finalized when all experts were in agreement, resulting in 48 items to implement in the data collection.

@@

colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)
```

@@

reduced.model.5F.1 <- dplyr::select(EFA.data ,
                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))

@@

reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))

@@

Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item7, item8, item9) 
Five.F3 <-  dplyr::select(EFA.data, item27, item3,item40, item30, item41)
Five.F4 <-  dplyr::select(EFA.data, item33,item32,item35, item37, item38)
Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item4, item1, item26)

@@

```{r gtvis, include =F}
## Recoding sem.data$item8
gt.data <- sem.data
gt.data$item8 <- as.character(gt.data$item8)
gt.data$item8 <- fct_recode(gt.data$item8,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)

@@

names(gt.data)[names(gt.data) == "item1"] <- "item01"
names(gt.data)[names(gt.data) == "item3"] <- "item03"
names(gt.data)[names(gt.data) == "item4"] <- "item04"
names(gt.data)[names(gt.data) == "item7"] <- "item07"
names(gt.data)[names(gt.data) == "item8"] <- "item08"
names(gt.data)[names(gt.data) == "item9"] <- "item09"

@@

## Recoding CFA.data$item8 into CFA.data$Ritem8
CFA.data$Ritem8 <- as.character(CFA.data$item8)
CFA.data$Ritem8 <- fct_recode(CFA.data$Ritem8,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
CFA.data$Ritem8 <- as.numeric(as.character(CFA.data$Ritem8))

@@

LB.model.Cor.1 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1 
                       a1==a2
                       a3==a4"

@@

```{r CFA23withMI, include=FALSE}
LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1 
                       a1==a2
                       a3==a4
                item30 ~~  item41
                       "

@@

```{r simulation, eval=FALSE, include=FALSE}
library("simsem")
pop.model <- "F1 =~ a1*item16 + .95*item36 + a2*item17
                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item7+ .50*Ritem8+ .49*item9
                 F3 =~  .78*item27+ .77*item3+ .68*item40 + .13*item30 + .20*item41
                 F4 =~ a3*item32 + .63*item35 + .33*item38+ a4*item33 
                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item4+ .22*item1 
                       a1==a2
                       a3==a4
                item30 ~~ .82*item41
F1~~1*F1
F2~~1*F2
F3~~1*F3
F4~~1*F4
F5~~1*F5
"

@@

semPaths (fit.Cor.2 , 
          what= "std",
          #whatLabels = "std",
          intercepts = F,
          #style ="lisrel",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,
          sizeMan2 = 1.5,
          sizeLat = 8,
          #edge.color = "black",
          thresholds = FALSE,
          equalizeManifests =T,
          fade = FALSE,
          edge.label.cex = .65,
          exoCov = FALSE)

@@

```{r Invariancedetail, include=FALSE}
# Configural invariance ####
configural <- cfa(model = LB.model.Cor.2,
                  data = invariance.data,
                  group = "English_Speaking",
                  ordered =   names(CFA.data),
                  estimator = "WLSMV")

@@

```{r IRTdata, include=FALSE}
## Recoding sem.data$item8 into sem.data$Ritem8
sem.data$Ritem8 <- as.character(sem.data$item8)
sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
# Recoding sem.data$item26 
sem.data$Ritem26 <- as.character(sem.data$item26)
sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))

@@

F2 <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)

F3 <- sem.data %>% 
 dplyr::select(item27, item3,  item40,  item30,  item41)

@@

F5 <- sem.data %>% 
  dplyr::select(item46, item45, item25, item4, item1 )

@@

## Plot grid ####
library(cowplot)
OCC <- plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
          labels = "AUTO", label_size = 10)

Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10)
```

```{r saveiteminfo, eval=FALSE, include=FALSE}
jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10,align = "v",ncol = 2)

dev.off()
```

```{r IRTreliability, include=FALSE}
#conditional reliability
F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F2.reliability <- plot(F2_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F3.reliability <- plot(F3_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F4.reliability <- plot(F4_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )

@@

```{r iteminfo, include=F, warning=F}
F1_item1<- plot(F1_fit, type = "infotrace", 
                    facet_items = T, which.items = 1, main = "")

@@

```{r shortIRT, include=FALSE}
F1 <- sem.data %>% 
  dplyr::select(item16, item36,  item17)
F2.redu <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
F3.redu <- sem.data %>% 
 dplyr::select(item27, item3,  item40)

@@

```{r scalechar, eval=FALSE, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="120%", out.width="100%"}

@@

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8, item9))

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F3.Total = sum(item27, item3,  item40))

>>>>

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

@@

```{r relscale, include=F, warning=F, message=F}

relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")

```{r reltab2}
relevant.scale.data %>%
   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
  kable_styling(latex_options = c("repeat_header", "scale_down")) %>% 
  column_spec(1:6, width = "2cm")

@@

## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam
names(sem.data)[names(sem.data) == "item1"] <- "item01"
names(sem.data)[names(sem.data) == "item2"] <- "item02"
names(sem.data)[names(sem.data) == "item3"] <- "item03"
names(sem.data)[names(sem.data) == "item4"] <- "item04"
names(sem.data)[names(sem.data) == "item5"] <- "item05"
names(sem.data)[names(sem.data) == "item6"] <- "item06"
names(sem.data)[names(sem.data) == "item7"] <- "item07"
names(sem.data)[names(sem.data) == "item8"] <- "item08"
names(sem.data)[names(sem.data) == "item9"] <- "item09"
```

@@

To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales. However, no scales specifically measuring the behavioral component of light exposure were found (Table \@ref(tab:eltab)). Consequentially we pursued to introduce a new openly available scale to address this research gap. For this purpose an expert researcher panel from the fields of chronobiology, light research, neuroscience and psychology (including seven of the authors, see authors roles) generated and collected preliminary item ideas. Special attention was paid to design items circumscribed to assess light exposure *behavior* as opposed to subjective measurements of the light environment (cf.[@eklund1996development] & [@dianat2013objective]) and semi-quantitive assesments of light sources' illuminance (cf. [@bajaj2011validation]) in order to maintain content validity. In a collective effort the generated items were then peer-reviewed,  amended, unified, and complemented with a suitable response scale (5 point Likert-scale ranging from 1 "Never/Does not apply/I don’t know" to 5 "Always"). This process was finalized when all experts were in agreement, resulting in 48 items to implement in the data collection.

@@

colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
rownameprefix <- "Item"
rownamesufix <- seq(01:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)
rownames(Des.combined)[rownames(Des.combined) == "Item1"] <- "Item01"
rownames(Des.combined)[rownames(Des.combined) == "Item2"] <- "Item02"
rownames(Des.combined)[rownames(Des.combined) == "Item3"] <- "Item03"
rownames(Des.combined)[rownames(Des.combined) == "Item4"] <- "Item04"
rownames(Des.combined)[rownames(Des.combined) == "Item5"] <- "Item05"
rownames(Des.combined)[rownames(Des.combined) == "Item6"] <- "Item06"
rownames(Des.combined)[rownames(Des.combined) == "Item7"] <- "Item07"
rownames(Des.combined)[rownames(Des.combined) == "Item8"] <- "Item08"
rownames(Des.combined)[rownames(Des.combined) == "Item9"] <- "Item09"
```

@@

reduced.model.5F.1 <- dplyr::select(EFA.data ,
                                    -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14))

@@

reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14, item34, item47, item21, item13))

@@

Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item07, item08, item09) 
Five.F3 <-  dplyr::select(EFA.data, item27, item03,item40, item30, item41)
Five.F4 <-  dplyr::select(EFA.data, item33,item32,item35, item37, item38)
Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item04, item01, item26)

@@

```{r gtvis, include =F}
## Recoding sem.data$item8
gt.data <- sem.data
gt.data$item08 <- as.character(gt.data$item08)
gt.data$item08 <- fct_recode(gt.data$item08,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)

@@

@@

## Recoding CFA.data$item8 into CFA.data$Ritem8
CFA.data$Ritem08 <- as.character(CFA.data$item08)
CFA.data$Ritem08 <- fct_recode(CFA.data$Ritem08,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
CFA.data$Ritem08 <- as.numeric(as.character(CFA.data$Ritem08))

@@

LB.model.Cor.1 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item07+ Ritem08+ item09
                 F3 =~  item27+ item03+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item04+ item01 
                       a1==a2
                       a3==a4"

@@

```{r CFA23withMI, include=FALSE}
LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item07+ Ritem08+ item09
                 F3 =~  item27+ item03+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item04+ item01 
                       a1==a2
                       a3==a4
                item30 ~~  item41
                       "

@@

```{r simulation, eval=FALSE, include=FALSE}
library("simsem")
pop.model <- "F1 =~ a1*item16 + .95*item36 + a2*item17
                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item07+ .50*Ritem08+ .49*item09
                 F3 =~  .78*item27+ .77*item03+ .68*item40 + .13*item30 + .20*item41
                 F4 =~ a3*item32 + .63*item35 + .33*item38+ a4*item33 
                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item04+ .22*item01 
                       a1==a2
                       a3==a4
                item30 ~~ .82*item41
F1~~1*F1
F2~~1*F2
F3~~1*F3
F4~~1*F4
F5~~1*F5
"

@@

semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="lisrel",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =6,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          exoCov = FALSE,
          centerLevels = T,
          edge.color="black",
          label.scale=T,
          label.cex=1, #Font of factor and item name
          residuals=FALSE,
           exoVar=FALSE,
          fixedStyle=6, #Style of arrow (guide item)
          freeStyle=1#Style of arrow (other item), #XKCD = TRUE

          )

@@

```{r Invariancedetail, include=FALSE}

LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item07+ Ritem08+ item09
                 F3 =~  item27+ item03+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item04+ item01 
                       a1==a2
                       a3==a4
                item30 ~~  item41
                       "  
# Configural invariance ####
configural <- cfa(model = LB.model.Cor.2,
                  data = invariance.data,
                  group = "English_Speaking",
                  ordered =   names(CFA.data),
                  estimator = "WLSMV")

@@

```{r IRTdata, include=FALSE}
## Recoding sem.data$item8 into sem.data$Ritem8
sem.data$Ritem08 <- as.character(sem.data$item08)
sem.data$Ritem08 <- fct_recode(sem.data$Ritem08,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem08 <- as.numeric(as.character(sem.data$Ritem08))
# Recoding sem.data$item26 
sem.data$Ritem26 <- as.character(sem.data$item26)
sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))

@@

F2 <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item07, Ritem08, item09)

F3 <- sem.data %>% 
 dplyr::select(item27, item03,  item40,  item30,  item41)

@@

F5 <- sem.data %>% 
  dplyr::select(item46, item45, item25, item04, item01 )

@@

```{r IRTreliability, eval=FALSE, include=FALSE}
#conditional reliability
F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F2.reliability <- plot(F2_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F3.reliability <- plot(F3_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F4.reliability <- plot(F4_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )

@@

```{r iteminfo, eval=FALSE, warning=FALSE, include=FALSE}
#Not used in the manuscript

F1_item1<- plot(F1_fit, type = "infotrace", 
                    facet_items = T, which.items = 1, main = "")

@@

```{r shortIRT, include=FALSE}
F1 <- sem.data %>% 
  dplyr::select(item16, item36,  item17)
F2.redu <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item07, Ritem08, item09)
F3.redu <- sem.data %>% 
 dplyr::select(item27, item03,  item40)

@@

```{r scalechar, eval=FALSE, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="120%", out.width="100%"}
#not used in the manuscript

@@

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F2.Total = sum(item11,  item10 , item12, item07, Ritem08, item09))

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F3.Total = sum(item27, item03,  item40))
